An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling

### 2017-04-21 paper.tex
Fix typo

\begin{abstract}
A real-time, Linux-based testbed, which we have developed for empirically evaluating multiprocessor
scheduling hehavior is presented, along with various enhancements that remove some of the fundamental
barriers to eliminate potential latency. Both raw performance and schedulability are considered for
hard real-time constraints. To our knowledge, this paper is the first attempt by anyone to obtain
comprehensive performance results regarding the scheduler and its interaction with external events.
\end{abstract}

>>>>

\begin{abstract}
A real-time, Linux-based testbed, which we have developed for empirically evaluating multiprocessor
scheduling behavior is presented, along with various enhancements that remove some of the fundamental
barriers to eliminate potential latency. Both raw performance and schedulability are considered for
hard real-time constraints. To our knowledge, this paper is the first attempt by anyone to obtain
comprehensive performance results regarding the scheduler and its interaction with external events.
\end{abstract}
